Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants \thanks{Supported by EPSRC grant EP/J012564/1 and ERC project 280053 (CPROVER).}

### 2017-02-02 hscc2017/paper.tex
added unique ID for each plant

\begin{table}
\centering
\scalebox{0.8}{
\begin{tabular}{| r | c | l | r r || r | r |}
\hline
\# & Plant  & Benchmark                  & $I$ & $F$
   & 2-stage & 1-stage
    \\\hline\hline
1  & $G_1$  & CrsControl02
            &   4 &  16 & 12\,s   & 67\,s     \\
2  & $G_1$  & CrsControl02$^\dagger$
            &   4 &  16 & 14600\,s   & 52\,s     \\
3  & $G_2$  & SpgMsDamper
            &  15 &  16 & 52\,s   & 318\,s     \\
4  & $G_2$  & SpgMsDamper$^\dagger$
            &  15 &  16 & \xmark  & \xmark    \\
5  & $G_3$  & SatelliteB2
            &   3 &   7 & 36\,s    & \xmark     \\
6  & $G_3$  & SatelliteB2$^\dagger$
            &   3 &   7 & \xmark  & 4111\,s  \\
7  & $G_3$  & SatelliteC2
            &   3 &   5 & 3\,s    & 205\,s    \\
8  & $G_3$  & SatelliteC2$^\dagger$
            &   3 &   5 & 50\,s  & 1315\,s    \\
9  & $G_4$  & Cruise
            &   3 &   7 & 1\,s  & 1\,s    \\
10 & $G_5$  & DC Motor
            &   3 &   7 & 1\,s  & 10\,s    \\
11 & $G_6$  & DC servomotor
            &   4 &  11 & 46\,s  & \xmark    \\
12 & $G_7$  & Doyleetal
            &   4 &  11 & 8769\,s  & \xmark    \\
13 & $G_8$  & Helicopter
            &   3 &   7 & 44\,s  & \xmark    \\
14 & $G_9$  & Pendulum
            &   3 &   7 & 1\,s  & 14826\,s    \\
15 &$G_{10}$& Suspension
            &   3 &   7 & 1\,s  & 5\,s    \\
16 &$G_{11}$& Tapedriver
            &   3 &   7 & 1\,s  & 1\,s    \\
17 &$G_{12a}$& a\_ST1\_IMPL1
            &  16 &   4 & 11748\,s & \xmark   \\
18 &$G_{12a}$& a\_ST1\_IMPL2
            &  16 &   8 & 351\,s  & \xmark   \\
19 &$G_{12a}$& a\_ST1\_IMPL3
            &  16 &  12 & 8772\,s   & \xmark   \\
20 &$G_{12b}$& a\_ST2\_IMPL1
            &  16 &   4 & 1128\,s  & \xmark   \\
21 &$G_{12b}$& a\_ST2\_IMPL2$^{*}$
            &  16 &   8 & \xmark  & \xmark    \\
22 &$G_{12b}$& a\_ST2\_IMPL3
            &  16 &  12 & 15183\,s & \xmark   \\ 
23 &$G_{12c}$& a\_ST3\_IMPL1$^{*}$
            &  16 &   4 & \xmark & \xmark   \\\hline
\end{tabular}}\\[0.2ex]
\caption{\tool results ({\xmark} = time-out, $\dagger$ = 
uncertainty)
\label{tab:results}}
\end{table}
%---------------------------------

>>>>

\begin{table}
\centering
\scalebox{0.8}{
\begin{tabular}{| r | c | l | r r || r | r |}
\hline
\# & Plant  & Benchmark                  & $I$ & $F$
   & 2-stage & 1-stage
    \\\hline\hline
1  & $G_{1a}$  & CrsControl02
            &   4 &  16 & 12\,s   & 67\,s     \\
2  & $G_{1b}$  & CrsControl02$^\dagger$
            &   4 &  16 & 14600\,s   & 52\,s     \\
3  & $G_{2a}$  & SpgMsDamper
            &  15 &  16 & 52\,s   & 318\,s     \\
4  & $G_{2b}$  & SpgMsDamper$^\dagger$
            &  15 &  16 & \xmark  & \xmark    \\
5  & $G_{3a}$  & SatelliteB2
            &   3 &   7 & 36\,s    & \xmark     \\
6  & $G_{3b}$  & SatelliteB2$^\dagger$
            &   3 &   7 & \xmark  & 4111\,s  \\
7  & $G_{3c}$  & SatelliteC2
            &   3 &   5 & 3\,s    & 205\,s    \\
8  & $G_{3d}$  & SatelliteC2$^\dagger$
            &   3 &   5 & 50\,s  & 1315\,s    \\
9  & $G_4$  & Cruise
            &   3 &   7 & 1\,s  & 1\,s    \\
10 & $G_5$  & DC Motor
            &   3 &   7 & 1\,s  & 10\,s    \\
11 & $G_6$  & DC servomotor
            &   4 &  11 & 46\,s  & \xmark    \\
12 & $G_7$  & Doyleetal
            &   4 &  11 & 8769\,s  & \xmark    \\
13 & $G_8$  & Helicopter
            &   3 &   7 & 44\,s  & \xmark    \\
14 & $G_9$  & Pendulum
            &   3 &   7 & 1\,s  & 14826\,s    \\
15 &$G_{10}$& Suspension
            &   3 &   7 & 1\,s  & 5\,s    \\
16 &$G_{11}$& Tapedriver
            &   3 &   7 & 1\,s  & 1\,s    \\
17 &$G_{12a}$& a\_ST1\_IMPL1
            &  16 &   4 & 11748\,s & \xmark   \\
18 &$G_{12a}$& a\_ST1\_IMPL2
            &  16 &   8 & 351\,s  & \xmark   \\
19 &$G_{12a}$& a\_ST1\_IMPL3
            &  16 &  12 & 8772\,s   & \xmark   \\
20 &$G_{12b}$& a\_ST2\_IMPL1
            &  16 &   4 & 1128\,s  & \xmark   \\
21 &$G_{12b}$& a\_ST2\_IMPL2$^{*}$
            &  16 &   8 & \xmark  & \xmark    \\
22 &$G_{12b}$& a\_ST2\_IMPL3
            &  16 &  12 & 15183\,s & \xmark   \\ 
23 &$G_{12c}$& a\_ST3\_IMPL1$^{*}$
            &  16 &   4 & \xmark & \xmark   \\\hline
\end{tabular}}\\[0.2ex]
\caption{\tool results ({\xmark} = time-out, $\dagger$ = 
uncertainty)
\label{tab:results}}
\end{table}
%---------------------------------
